### 2015-05-08 intro.tex
update

In this paper, we present \whoop, a new fully automatic approach that (i) statically analyses device drivers written in the C language for data races and (ii) exploits the race-related results from the static analysis to accelerate bug-finding. \whoop is empowered by \emph{static pairwise lockset analysis}, a novel technique for automatically verifying the absence of data races in device drivers. The key idea behind our approach is that a driver can be proven free from data races by (i) deriving a sound \emph{sequential} model that \emph{over-approximates} the originally concurrent program, (ii) instrumenting it for lockset analysis and race-checking, and (iii) asserting that all accesses to the same shared resource are protected by at least one common lock. The immediate benefit is that our approach not only avoids reasoning about thread interleavings, and thus has the potential to scale well, but also allows the reuse of existing successful sequential verification techniques.

We then show that by exploiting the race-freedom guarantees that our static analysis provides, we can achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012solver}, a state-of-the-art bug-finder that is used by Microsoft to analyze device drivers, as well as other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers available in the 4.0 Linux kernel distribution.

@@

To summarize, our contributions are as follows:
\begin{itemize}
\item We present \whoop, a new fully automatic approach for analyzing device drivers for data races and accelerating bug-finding.
\item We discuss static pairwise lockset analysis,  a sound and scalable technique for automatically verifying the absence of data races in device drivers.
\item We show that we can achieve a sound partial-order reduction using our technique and significantly speedup \corral, a state-of-the-art bug-finder.
\item We analyze \sizeOfBenchmarks Linux drivers, showing that \whoop is efficient in race-checking and accelerating \corral.
\end{itemize}

>>>>

In this paper, we present \whoop, a new fully automatic approach that (i) statically analyzes device drivers written in the C language for data races and (ii) exploits the race-related results from the symbolic analysis to accelerate bug-finding. \whoop is empowered by \emph{symbolic pairwise lockset analysis}, a novel technique for automatically verifying the absence of data races in device drivers. The key idea behind our approach is that a driver can be proven free from data races by (i) deriving a sound \emph{sequential} model that \emph{over-approximates} the originally concurrent program, (ii) instrumenting it for lockset analysis and race-checking, and (iii) asserting that all accesses to the same shared resource are protected by at least one common lock. The immediate benefit is that our approach not only avoids reasoning about thread interleavings, and thus has the potential to scale well, but also allows the reuse of existing successful sequential verification techniques.

We then show that by exploiting the race-freedom guarantees that our symbolic analysis provides, we can achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012solver}, a state-of-the-art bug-finder that is used by Microsoft to analyze device drivers, as well as other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers available in the 4.0 Linux kernel distribution.

@@

To summarize, our contributions are as follows:
\begin{itemize}
\item We present \whoop, a new fully automatic approach for analyzing device drivers for data races and accelerating bug-finding.
\item We discuss symbolic pairwise lockset analysis,  a sound and scalable technique for automatically verifying the absence of data races in device drivers.
\item We show that we can achieve a sound partial-order reduction using our technique and significantly speedup \corral, a state-of-the-art bug-finder.
\item We analyze \sizeOfBenchmarks Linux drivers, showing that \whoop is efficient in race-checking and accelerating \corral.
\end{itemize}
